Paper 2: Vitamin D

### 2017-09-19 doc/vitaminD.Rmd
plot interaction terms

gee_vitd_baseline <- ds %>% 
  prep_mason_data_kidney() %>% 
  mason_gee(y = c("VitaminD"),
            x = "udbpBase",
            covars = c("MonthsFromBaseline", "ageBase", "Sex", "Ethnicity", "BMI", "dmStatus", "Season"),
            intvar = "Season")

@@

plot_gee_results_vitd(gee_vitd_baseline,
                 yvars = c("uAlbumin:creatinine (mg/mmol)", 
                           "eGFR (ml/min/1.73m^2)"))
```

>>>>

gee_vitd_baseline <- ds %>% 
  prep_mason_data_vitd() %>% 
  mason_gee(y = c("VitaminD"),
            x = "udbpBase",
            covars = c("MonthsFromBaseline", "ageBase", "Sex", "Ethnicity", "BMI", "dmStatus", "Season"),
            intvar = "Season") %>% 
  mason::polish_renaming(rename_gee_vitd)

@@

plot_gee_results_vitd(gee_vitd_baseline,
                 yvars = "Serum 25(OH)D (nmol/L)")

# Plot interaction ---------------------------------------------------

dsBase %>% 
  ggplot2::ggplot(ggplot2::aes(x = log(udbpCrRatio), y = VitaminD, colour = Season)) +
  ggplot2::geom_point(colour = "grey", alpha = 0.5) +
  ggplot2::geom_smooth(method = "lm") +
  ggplot2::xlab("log uVDBP:creatinine (ug/mmol)") +
  ggplot2::ylab("Serum 25(OH)D (nmol/L)")
```

```{r}
gee_vitd_baseline <- ds %>% 
  prep_mason_data_vitd() %>% 
  mason_gee(y = c("VitaminD"),
            x = "udbpBase",
            covars = c("MonthsFromBaseline", "ageBase", "Sex", "Ethnicity", "BMI", "dmStatus", "PTH"),
            intvar = "PTH") %>% 
  mason::polish_renaming(rename_gee_vitd)

# Plot interaction ---------------------------------------------------

dsBase %>% 
  interac_plot(yvar = "VitaminD",
               intvar = "Season",
               ylab = "Serum 25(OH)D (nmol/L)")
```
